Verifying Demonstrations

### 2017-10-04 protocol.tex
Adds placeholder caption for protocol message sequence diagram
Fixes minor details in proof-share figure

      \path[every node/.style={font=\small}]
      (pid) edge node [anchor=east] {$\in$} (proof)
      (ts) edge node [anchor=east] {$\in$} (proof)
      (l) edge node [anchor=east] {$\in$} (proof)
      (wid) edge node [anchor=east] {$\in$} (proof)
      (wsig) edge node [anchor=east] {$\in$} (proof)
      ;

@@

\begin{figure}
  \centering
  \dots
  \caption{%
    \dots
  }%
  \label{fig:ProtocolOverview}
\end{figure}

>>>>

      \path[every node/.style={font=\small}]
      (pid) edge node [anchor=south east] {$\in$} (proof)
      (wid) edge node [anchor=east] {$\in$} (proof)
      (ts) edge node [anchor=east] {$\in$} (proof)
      (l) edge node [anchor=west] {$\in$} (proof)
      (wsig) edge node [anchor=south west] {$\in$} (proof)
      ;

@@

\begin{figure}
  \centering
  \dots
  \caption{%
    An overview of message exchanges.
  }%
  \label{fig:ProtocolOverview}
\end{figure}
